### 2016-05-03 ch02-qlogms/excitation-design.tex
More small things

  \subsubsection{Exploiting the grid misalignment between the system and the grid}
  Denote $G(\omega; \wn)$ a second-order sub-system as in \eqref{eq:excitation:secondOrderSubsystem} with natural frequency $\wn$, damping ratio $\damping$ and static gain $\dc$, and zero at $\wz$.
  Similarly, $G(\omega; m\wn)$ where $m \in \RealNumbersWithoutZero$ is a second order sub-system that shares the same parameters, except its natural frequency which is situated at $m\wn$.

>>>>

  \subsubsection[Exploiting the grid misalignment]{Exploiting the grid misalignment between the system and the grid}
  Denote $G(\omega; \wn)$ a second-order sub-system as in \eqref{eq:excitation:secondOrderSubsystem} with natural frequency $\wn$, damping ratio $\damping$ and static gain $\dc$, and zero at $\wz$.
  Similarly, $G(\omega; m\wn)$ where $m \in \RealNumbersWithoutZero$ is a second order sub-system that shares the same parameters, except its natural frequency which is situated at $m\wn$.
